---
title: "Data Analysis for: How Two- and Three-Year-Olds Coordinate Decisions in Dyads and Triads"
output: html_document
date: "2026-03-09"
---

```{r globals, include=FALSE}
start <- Sys.time()

#### globals ####
library(brms)      # modeling
library(flextable) # tables
library(ggpattern) # visualization aesthetics
library(janitor)   # data operations
library(officer)   # tables
library(parallel)  # parallelization
library(patchwork) # plots
library(psych)     # reliability
library(readxl)    # data import
library(scales)    # plots
library(tidybayes) # inference
library(tidyverse) # data operations

options(contrasts = c("contr.treatment", "contr.poly")) # treatment coding

n_epred_draws <- 2000 # n draws of expected values
n_length <- 30 # n bins for continuous variables in prediction grid
```

```{r import-data, include=FALSE}

tsa_data_raw <- read_excel("data/tsa_data.xlsx") # import group data
tsa_reliability_expanded <- read_excel("data/tsa_reliability_expanded.xlsx") # import expanded reliability data
tsa_communication0 <- read_excel("data/tsa_comm.xlsx") # import expanded reliability data

```

### DATA CLEANING ###
```{r data preparation}

tsa_data000 <- tsa_data_raw %>% # create group_mean_age to join later
  select(group, participant_age) %>% 
  clean_names() %>%
  group_by(group) %>% 
  mutate(group_mean_age = mean(participant_age)) %>% 
  ungroup() %>% 
  distinct(group, group_mean_age) %>% 
  rename(group_id = group)

tsa_data00 <- tsa_data_raw %>% 
  left_join(tsa_data000, by = "group_id") %>% 
  group_by(group_id) %>% 
  mutate(trial = row_number()) %>%
  ungroup() %>% 
  mutate(age_factor = as.factor(age),
         trial = as.factor(trial),
         outcome = case_when(outcome == 1 ~ "successful",
                             outcome == 0 ~ "unsuccessful",
                             T ~ NA),
         across(c(where(is.character)), ~ as.factor(.)), # all character vars (and age) to factors
         group_mean_age_standardized = as.numeric(scale(group_mean_age)), # we can simply standardize because every group contributed 4 observations
         outcome = relevel(outcome, ref = "unsuccessful"), # to model pr(success)
         #recoding method variable to reflect order presented in manuscript
         method = factor(case_when(method == 0 ~ 0,
                                   method == 1 ~ 1, 
                                   method == 2 ~ 3, 
                                   method == 3 ~ 4, 
                                   method == 4 ~ 2,
                                   T ~ NA)), # replaced as.numeric(method) with NA -- produces identical df's but NA is more readable
         information_binary = ifelse(method == 4, 1, 0)) %>% 
  rename(strategy = method)

tsa_demo <- tsa_data00 %>% 
  select(group, participant, participant_age) %>% 
  mutate(participant = paste0(group, str_to_lower(as.character(participant))))

tsa_data0 <- tsa_data00 %>% 
  mutate(
    collab_yesno = factor(
      case_when(
        strategy == "4" ~ "collaborative",
        strategy != "4" ~ "individualistic",
        TRUE ~ NA_character_),
      levels = c("collaborative", "individualistic")), # exclude unsuccessful groups
    strategy_recoded = case_when(
      strategy == "4" ~ "1", 
      strategy != "4" ~ "0",
      is.na(strategy) ~ "0"),
    trial_type = ifelse(
      trial != "4", 
      "test", 
      "generalization"), # test or generalization trial
    color_pattern = case_when(
      color_pattern == "0" ~ "no_pattern",
      color_pattern == "1" ~ "first_successful",
      color_pattern == "2" ~ "alternate",
      TRUE ~ NA_character_),
    group_size_num = case_when(
      group_size == "dyad" ~ 2, 
      group_size == "triad" ~ 3))

#calculate communication per prompt
tsa_data <- tsa_data0 %>% 
  mutate(n_inits_perprompt = communication / (prompt), 
         n_inits_perprompt_stand = as.numeric(scale(n_inits_perprompt)))

communication_cols <- c(
  "directive",
  "suggestive",
  "correct_partners",
  "describe_own_choice",
  "name_point_show_color_or_animal",
  "request_info",
  "direct_attention"
)

tsa_communication <- tsa_communication0 %>%
  mutate(
    communication_type = case_when(
      directive == 1 ~ "directive",
      suggestive == 1 ~ "suggestive",
      correct_partners == 1 ~ "correct_partners",
      describe_own_choice == 1 ~ "describe_own_choice",
      name_point_show_color_or_animal == 1 ~ "name_point_show_color_or_animal",
      request_info == 1 ~ "request_info",
      direct_attention == 1 ~ "direct_attention",
      TRUE ~ NA_character_
    )
  )

# checks for final data frame
# tsa_data %>% count(group_id)
# tsa_data %>% count(outcome)
# tsa_data %>% count(group_id, age_factor)
# tsa_data %>% count(age_factor, group_size, trial)

```

### DESCRIPTIVES ###
```{r basic descriptives}

tsa_data %>% # age by condition descriptives
  group_by(age_factor) %>%
  summarize(mean = mean(group_mean_age),
            sd = sd(group_mean_age),
            min = min(group_mean_age),
            sd_minus = mean - sd,
            sd_plus = mean + sd,
            max = max(group_mean_age),
            .groups = "drop")

tsa_data %>% # success descriptives
  group_by(group_size, age_factor) %>%
  count(outcome) %>% 
  mutate(proportion = n / sum(n))

tsa_data %>% # engagement descriptives
  group_by(group_size, age_factor) %>%
  count(c_engagement) %>% 
  mutate(proportion = n / sum(n))

tsa_data %>% # location descriptives
  group_by(age_factor) %>%
  count(location) %>% 
  mutate(proportion = n / sum(n))

tsa_data %>% # prompt stats
  select(group_size, age_factor, prompt) %>%
  mutate(prompt = replace_na(prompt, 7)) %>%
  group_by(age_factor, group_size) %>%
  summarize(mean = mean(prompt),
            sd = sd(prompt))

# communication descriptives

tsa_communication %>%
  filter(!is.na(audience)) %>%
  count(age) %>%
  group_by(age) %>%
  mutate(
    total = sum(n),
    prop = n / total,
    percent = prop * 100
  )

tsa_communication %>%
  filter(!is.na(communication_type)) %>%
  count(age, communication_type) %>%
  group_by(age) %>%
  mutate(
    total = sum(n),
    prop = n / total,
    percent = prop * 100
  )

tsa_communication %>%
  filter(!is.na(communication_type)) %>%
  count(age, communication_type) %>%
  ggplot(
    aes(
      x = communication_type,
      y = n,
      fill = age
    )
  ) +
  geom_col(
    width = 0.8,
    position = position_dodge(width = 0.8)
  ) +
  geom_text(
    aes(label = n),
    position = position_dodge(width = 0.8),
    hjust = -0.2,
    size = 3
  ) +
  coord_flip() +
  labs(
    x = "Communication type",
    y = "Number of communication acts",
    fill = "Age"
  ) +
  theme_minimal()

tsa_communication %>%
  filter(!is.na(audience)) %>%
  count(age, audience) %>%
  group_by(age) %>%
  mutate(
    total = sum(n),
    prop = n / total,
    percent = prop * 100
  )

tsa_communication %>%
  filter(!is.na(key)) %>%
  count(age, key) %>%
  group_by(age) %>%
  mutate(
    total = sum(n),
    prop = n / total,
    percent = prop * 100
  )

tsa_communication %>%
  filter(!is.na(key)) %>%
  count(age, key, audience) %>%
  group_by(age, audience) %>%
  mutate(
    total = sum(n),
    prop = n / total,
    percent = prop * 100
  )


tsa_data %>% # n initiations
  select(group_size, age_factor, outcome, n_inits_perprompt) %>%
  group_by(outcome) %>%
  summarize(mean = mean(n_inits_perprompt),
            sd = sd(n_inits_perprompt))

tsa_data %>% # n initiations
  select(group_size, age_factor, outcome, n_inits_perprompt) %>%
  group_by(group_size) %>%
  summarize(mean = mean(n_inits_perprompt),
            sd = sd(n_inits_perprompt))

tsa_data %>% # n initiations
  select(group_size, age_factor, outcome, n_inits_perprompt) %>%
  group_by(age_factor) %>%
  summarize(mean = mean(n_inits_perprompt),
            sd = sd(n_inits_perprompt))

```

### RELIABILITY ###
```{r reliability}
##check this lapply as factor with jared
tsa_reliability_expanded[] <- lapply(tsa_reliability_expanded, as.factor)

#prompts reliability
prompts_reliability <- as.matrix(tsa_reliability_expanded[, c("B_prompts", "A_prompts")])
cohen.kappa(prompts_reliability[, c("B_prompts", "A_prompts")])

mean(as.numeric(tsa_reliability_expanded$B_prompts) == as.numeric(tsa_reliability_expanded$A_prompts),
     na.rm = TRUE) * 100

#outcome reliability
outcome_reliability <- as.matrix(tsa_reliability_expanded[, c("B_outcome", "A_outcome")])
cohen.kappa(outcome_reliability[, c("B_outcome", "A_outcome")])

mean(tsa_reliability_expanded$B_outcome == tsa_reliability_expanded$A_outcome,
     na.rm = TRUE) * 100

#tactic/method reliability
tactic_reliability <- as.matrix(tsa_reliability_expanded[, c("B_tactic", "A_tactic")])
cohen.kappa(tactic_reliability[, c("B_tactic", "A_tactic")])

mean(tsa_reliability_expanded$B_tactic == tsa_reliability_expanded$A_tactic,
     na.rm = TRUE) * 100

#color reliability
color_reliability <- as.matrix(tsa_reliability_expanded[, c("A_color", "B_color")])
cohen.kappa(color_reliability[, c("A_color", "B_color")])

mean(tsa_reliability_expanded$B_color == tsa_reliability_expanded$A_color,
     na.rm = TRUE) * 100

#engagement reliability
engagement_reliability <- as.matrix(tsa_reliability_expanded[, c("A_engagement", "B_engagement")])
cohen.kappa(engagement_reliability[, c("A_engagement", "B_engagement")])

mean(tsa_reliability_expanded$B_engagement == tsa_reliability_expanded$A_engagement,
     na.rm = TRUE) * 100

#communication reliability
communication_reliability <- tsa_reliability_expanded %>%
  mutate(
    A_communication = as.numeric(A_communication),
    B_communication = as.numeric(B_communication),
    proportional_agreement = case_when(
      is.na(A_communication) | is.na(B_communication) ~ NA_real_,
      A_communication == 0 & B_communication == 0 ~ 1,
      TRUE ~ pmin(A_communication, B_communication) /
        pmax(A_communication, B_communication)))

communication_reliability %>%
  summarise(
    n_rows_included = sum(!is.na(proportional_agreement)),
    n_exact_matches = sum(
      A_communication == B_communication,
      na.rm = TRUE),
    n_disagreements = sum(
      A_communication != B_communication,
      na.rm = TRUE),
    percent_agreement = mean(
      proportional_agreement,
      na.rm = TRUE) * 100)

```

# Priors and Sampler
```{r priors and sampler}
model_priors <- c(prior(normal(0, 1.00), class = Intercept),
                  prior(normal(0, 0.70), class = b),
                  prior(normal(0, 0.40), class = sd),
                  prior(lkj(2), class = cor))

func_brm <- function(formula,
                     data, 
                     priors = NULL, # default priors when none declared
                     family,
                     n_chains = 7, # n hmc chains (equals n - 1 cores on JV's machine),
                     adapt_delta = 0.9,
                     refresh = 1000) {
  brm(formula = formula,
      data = data,
      family = family,
      iter = 5000,
      warmup = 2000,
      chains = n_chains,
      cores = detectCores() - 1,
      control = list(adapt_delta = adapt_delta),
      prior = priors,
      refresh = refresh,
      seed = 27707 # reproducible sampler
      ) 
}
```

# Analyses
## Engagement

### Data Preparation
```{r engagement data preparation}
engagement_df0 <- tsa_data0 %>% # engagement stats (df to be modeled, below)
  select(group_id, trial, group_size, age_factor, ends_with("_engagement")) %>%
  pivot_longer(cols = ends_with("_engagement"), names_to = "participant", values_to = "engagement") %>%
  drop_na(engagement) %>% # drop NAs for third participants in dyads
  mutate(engagement_factor = as.factor(engagement),
         participant = str_remove(paste0(group_id, participant), "_engagement"))

engagement_df0 %>%
  group_by(engagement_factor) %>%
  count() %>%
  ungroup() %>%
  # group_by(group_size) %>%
  mutate(ratio = 100 * round(n / sum(n), 3)) %>% 
  ungroup()

engagement_df <- engagement_df0 %>% 
  filter(engagement_factor != "0")
```

### Model
```{r engagement model}
contrasts(engagement_df$engagement_factor)

mod_engagement <- func_brm(
  formula = engagement_factor ~ group_size + age_factor + (1 | group_id) + (1 | group_id:participant) + (1 | trial),
                           data = engagement_df,
                           prior = model_priors[-4,],
                           family = "bernoulli")
```

### Posterior Checks
```{r engagement posterior checks}
# pp_check(mod_engagement)
# plot(mod_engagement) # trace plots

func_bayesian_p_val <- function(mod, responsevar) {
  family <- mod$family$family                 # Detect family (for bernoulli or poisson -- categorical is computed separately)
  yrep <- posterior_predict(mod)              # Posterior predictive draws
  yobs <- as.numeric(mod$data[[responsevar]]) # Observed data
  if (family == "bernoulli") {                # Adjust for Bernoulli if needed
    yobs <- yobs - 1                          # assumes 1 = success, 0 = failure
  }
  T_obs_mean <- mean(yobs)                    # Compute summary statistics
  T_rep_mean <- apply(yrep, 1, mean)
  pvals = mean(T_rep_mean >= T_obs_mean) # Bayesian p-values
  print(pvals)
}

func_bayesian_p_val(mod = mod_engagement, responsevar = "engagement_factor")
```

## Coordination
### Data Preparation
```{r coordination data preparation}
# fig coordination data (coordination data)
df_fig_coord_data <- tsa_data %>%
  group_by(age_factor, group_size, group_id, outcome) %>% 
  count() %>% 
  mutate(n = ifelse(outcome == "unsuccessful" & n == 4, 0, n), # recode the 3 groups who failed all 4 times as n(successful) = 0
         outcome = ifelse(outcome == "unsuccessful" & n == 0, "successful", paste(outcome)), # recode "unsuccessful" into "successful" for rows n(successful) = 0
         age_factor_recoded = case_when(age_factor == "2" ~ "2-Year-Olds", age_factor == "3" ~ "3-Year-Olds"),
         group_size = str_to_title(group_size)) %>% 
  filter(outcome == "successful") %>% 
  ungroup() %>% 
  left_join(tsa_data %>% distinct(group_id, group_mean_age))

df_fig_coord_data %>% group_by(group_size, age_factor) %>% summarize(mean = mean(n), sd = sd(n))
  
ggplot(df_fig_coord_data,
       aes(x = fct_rev(group_size), y = n)) +
  geom_jitter(width = 0.25, height = 0.1, size = 3, alpha = 0.6, color = "forestgreen") +
  stat_summary(fun = mean, geom = "crossbar", color = "black", linewidth = .45) +
  facet_grid(~ age_factor_recoded) + 
  theme_classic(base_size = 16, base_family = "Times New Roman") +
  scale_y_continuous(breaks = 0:4, limits = c(-0.2, 4.2)) +
  labs(x = "Group Size",
       y = "Number of Successes") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))
# ggsave("figs/fig_coord_data.png", height = 3, width = 4)
```

### Models
```{r coordination models}
contrasts(tsa_data$outcome) # check that we're modeling pr(success)

mod_success <- func_brm(formula = outcome ~ 
                          group_size * group_mean_age_standardized + familiarity + location + (1 | group_id) + (1 | trial),
                        data = tsa_data,
                        family = "bernoulli",
                        priors = model_priors[-4,])

mod_success_comm <- func_brm(formula = outcome ~ n_inits_perprompt_stand * group_size + (n_inits_perprompt_stand | group_id) + (1 | trial),
                             data = tsa_data,
                             family = "bernoulli",
                             priors = model_priors)
```

### Posterior Checks
```{r coordination posterior checks}
# conditional_effects(mod_success)
# conditional_effects(mod_success_comm)
# plot(conditional_effects(mod_success_comm, effects = "n_inits_perprompt_stand:group_size"), plot = F)[[1]] +
# theme_classic(base_family = "Times New Roman", base_size = 15)
# plot(mod_success) # trace plots
# plot(mod_success_comm) # trace plots

pp_check(mod_success, "dens_overlay", ndraws = 100)
# pp_check(mod_success, "dens_overlay_grouped", ndraws = 1000, group = "group_size")
# pp_check(mod_success, "ecdf_overlay_grouped", ndraws = 1000, group = "group_size")
# pp_check(mod_success, "ecdf_overlay", ndraws = 100)

func_bayesian_p_val(mod = mod_success, responsevar = "outcome")
func_bayesian_p_val(mod = mod_success_comm, responsevar = "outcome")
```

### Results
#### Posterior Draws
```{r coordination posterior draws}
# prepare posterior prediction grids
newdata_mod_success <- crossing(group_size = (levels(mod_success$data$group_size)),
                                location = levels(mod_success$data$location),
                                familiarity = levels(mod_success$data$familiarity),
                                group_mean_age_standardized = seq(from = min(mod_success$data$group_mean_age_standardized), 
                                                                  to = max(mod_success$data$group_mean_age_standardized), 
                                                                  length.out = n_length), 
                                trial = levels(mod_success$data$trial)) %>% 
  mutate(across(c(group_size, trial, location), ~as.factor(.)))

newdata_mod_success_comm <- crossing(n_inits_perprompt_stand = seq(from = min(mod_success_comm$data$n_inits_perprompt_stand), 
                                                              to = max(mod_success_comm$data$n_inits_perprompt_stand), 
                                                              length.out = n_length),
                                     trial = levels(mod_success_comm$data$trial),
                                     group_size = levels(mod_success_comm$data$group_size)) %>% 
  mutate(across(where(is.character), ~as.factor(.)))

# draw posterior samples
epred_mod_success <- local({
  set.seed(27707) # reproducible subsampling of posterior draws
  epred_draws(mod_success, # draws of posterior model-predicted success rate
              newdata_mod_success,
              re_formula = ~(1 | trial), # generate predictions per trial level, marginalized across what we've learned about group-level variance (i.e., the other random intercept)
              ndraws = n_epred_draws)
}) %>%
  ungroup() %>% 
  mutate(
    group_mean_age_standardized = group_mean_age_standardized,
    group_mean_age = group_mean_age_standardized * sd(tsa_data$group_mean_age) + mean(tsa_data$group_mean_age),
    group_size = str_to_title(group_size),
    age_factor = factor(ifelse(group_mean_age >= 3, "3-Year-Olds", "2-Year-Olds")), # make categorical age var
    trial_type = factor(ifelse(trial != "4", "test", "generalization")),
    trial = as.integer(trial)) # checked to ensure that the factor maps correctly to the trial number

epred_mod_success_comm <- local({
  set.seed(27707) # reproducible subsampling of posterior draws
  epred_draws(mod_success_comm, # draws of posterior model-predicted success rate
              newdata_mod_success_comm,
              re_formula = ~(1 | trial), # generate predictions per trial level, marginalized across what we've learned about group-level variance (i.e., the other random intercept)
              ndraws = n_epred_draws)
}) %>%
  ungroup() %>% 
  mutate(
    n_inits_perprompt = n_inits_perprompt_stand * sd(tsa_data$n_inits_perprompt) + mean(tsa_data$n_inits_perprompt),
  )
```

#### Continuous Age
```{r coordination continuous age}
# marginal age and communication effect
func_mod_success_continuous <- function(df_draws, continuous_predictor){
  df <- df_draws %>%
    group_by(.draw) %>% # compute average effect
    summarize(slope = cov({{continuous_predictor}}, .epred) / var({{continuous_predictor}}), .groups = "drop")
  
  df %>%
    summarize(prop_gt = mean(slope > 0),
              hdi_lo = hdi(slope)[ncol(hdi(slope)) - 1], # rightmost HDI LB to safeguard against multimodality
              mean_slope = mean(slope),
              hdi_hi = hdi(slope)[ncol(hdi(slope))], # rightmost HDI UB to safeguard against multimodality
              .groups = "drop")
}

# do older children succeed more often than younger children, on average?
epred_mod_success_marginal_age_draws <- func_mod_success_continuous(epred_mod_success, group_mean_age)

# do more frequent talkers succeed more often than less frequent talkers, on average?
epred_mod_success_comm_marginal_comm_draws <- func_mod_success_continuous(epred_mod_success_comm, n_inits_perprompt)

# age contrasts
epred_mod_success_draws_slopes <- epred_mod_success %>%
  group_by(.draw, group_size) %>%
  summarize(age_slope = cov(group_mean_age, .epred) / var(group_mean_age),
            .groups = "drop")

epred_mod_success_draws_contrasts <- epred_mod_success_draws_slopes %>%
  compare_levels(age_slope, by = group_size) %>% 
  ungroup() %>% 
  mutate(group_size = "difference_age_slope")

bind_rows(epred_mod_success_draws_slopes, epred_mod_success_draws_contrasts) %>% 
  group_by(group_size) %>% 
  summarize(prop_gt = mean(age_slope > 0),
            hdi_lo = hdi(age_slope)[ncol(hdi(age_slope)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_age_slope = mean(age_slope),
            hdi_hi = hdi(age_slope)[ncol(hdi(age_slope))], # rightmost HDI UB to safeguard against multimodality
            .groups = "drop")

# bayesian johnson-neyman
bayes_jn_draws <- epred_mod_success %>% 
  group_by(.draw, group_size,  group_mean_age, group_mean_age_standardized) %>% 
  summarize(mean_epred = mean(.epred)) %>% 
  ungroup() %>% 
  group_by(group_mean_age, group_mean_age_standardized) %>% 
  compare_levels(mean_epred, by = "group_size") %>% 
  ungroup()

bayes_jn_draws_contrasts <- bayes_jn_draws %>% 
  group_by(group_mean_age, group_mean_age_standardized) %>% 
  summarize(prop_gt = mean(mean_epred > 0),
            ci_lo = quantile(mean_epred, .025),
            mean_mean_epred = mean(mean_epred),
            ci_hi = quantile(mean_epred, .975),
            .groups = "drop")

bayes_jn_draws_contrasts %>% print(n = Inf) # 3.20 years based on bins

age_zero <- bayes_jn_draws %>% # 3.17 years interpolated (via HDI, not CI -- CI only used for plotting)
  group_by(group_mean_age, group_mean_age_standardized) %>% 
  summarize(prop_gt = mean(mean_epred > 0),
            ci_lo = hdi(mean_epred)[[1]],
            mean_mean_epred = mean(mean_epred),
            ci_hi = hdi(mean_epred)[[2]],
            .groups = "drop") %>% 
  arrange(group_mean_age) %>% 
  with(approx(x = ci_hi,
              y = group_mean_age,
              xout = 0)$y)

paste(round(age_zero, 2), "years")

# supplement (sup fig1)
ggplot(bayes_jn_draws_contrasts,
       aes(x = group_mean_age,
           y = mean_mean_epred)) +
  geom_ribbon(data = ,
              aes(ymin = ci_lo,
                  ymax = ci_hi),
              alpha = 0.2) +
  geom_line(data = bayes_jn_draws_contrasts, linewidth = 1) +
  theme_classic(base_size = 18, base_family = "Times New Roman") +
  labs(x = "Age",
       y = "Difference in Predicted Success Rates") +
  geom_vline(xintercept = age_zero, linetype = 2, linewidth = .8, alpha = 1) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = .5, alpha = .5, color = "grey40") +
  scale_y_continuous(
    labels = function(x) sub("^(-?)0\\.", "\\1.", sprintf("%.1f", x)),
    breaks = pretty_breaks(3)) +
  theme(axis.title.y = element_text(size = 16))
# ggsave("figs/sup_fig2.png", width = 5, height = 4)
```

#### Categorical Age
```{r coordination categorical age}
epred_mod_success_categorical_draws <- epred_mod_success %>% 
  group_by(.draw, group_size, age_factor) %>% 
  summarize(mean_epred = mean(.epred), .groups = "drop") %>% # compute predicted success per age group and group size
  pivot_wider(names_from = age_factor, values_from = mean_epred) %>% 
  mutate(age_slope = `3-Year-Olds` - `2-Year-Olds`) %>%  # compute distribution over age effect within group size
  pivot_wider(names_from = group_size, values_from = c(`3-Year-Olds`, `2-Year-Olds`, age_slope)) %>% 
  mutate(difference_age_slope = age_slope_Triad - age_slope_Dyad) # compute distribution over interaction

epred_mod_success_categorical_draws %>% # summarize contrasts
  select(c(.draw, age_slope_Triad, age_slope_Dyad, difference_age_slope)) %>% 
  pivot_longer(cols = !.draw, names_to = "variable", values_to = "predicted_difference_age_slope") %>% 
  group_by(variable) %>%
  summarize(prop_gt = mean(predicted_difference_age_slope > 0),
            hdi_lo = hdi(predicted_difference_age_slope)[ncol(hdi(predicted_difference_age_slope)) - 1],
            mean_predicted_difference = mean(predicted_difference_age_slope),
            hdi_hi = hdi(predicted_difference_age_slope)[ncol(hdi(predicted_difference_age_slope))],
            .groups = "drop")

# marginal probabilities
epred_mod_success_bygroup_draws <- epred_mod_success %>% 
  group_by(.draw, age_factor, group_size) %>% # draws of predicted success rate in each combination of group_size and age_group, on average across location, trial, and age bins
  summarize(mean_epred = mean(.epred),
            .groups = "drop") 
summary_epred_mod_success_bygroup_draws <- epred_mod_success_bygroup_draws %>%
  group_by(age_factor, group_size) %>% 
  summarize(prop_gt = mean(mean_epred > 0.5),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            hdi_lo = hdi(mean_epred)[ncol(hdi(mean_epred)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_epred = mean(mean_epred),
            hdi_hi = hdi(mean_epred)[ncol(hdi(mean_epred))], # rightmost HDI UB to safeguard against multimodality
            .groups = "drop")

epred_mod_success_bylocation_draws <- epred_mod_success %>% 
  group_by(.draw, location) %>%
  summarize(mean_epred = mean(.epred),
            .groups = "drop") 
epred_mod_success_bylocation_draws %>%
  group_by(location) %>% 
  summarize(prop_gt = mean(mean_epred > 0.5),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            hdi_lo = hdi(mean_epred)[ncol(hdi(mean_epred)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_epred = mean(mean_epred),
            hdi_hi = hdi(mean_epred)[ncol(hdi(mean_epred))], # rightmost HDI UB to safeguard against multimodality
            .groups = "drop")
epred_mod_success_bylocation_draws_contrast <- epred_mod_success_bylocation_draws %>% 
  compare_levels(mean_epred, "location")
epred_mod_success_bylocation_draws_contrast %>% 
  summarize(prop_gt = mean(mean_epred > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            hdi_lo = hdi(mean_epred)[ncol(hdi(mean_epred)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_epred = mean(mean_epred),
            hdi_hi = hdi(mean_epred)[ncol(hdi(mean_epred))], # rightmost HDI UB to safeguard against multimodality
            .groups = "drop")

epred_mod_success_byfamiliarity_draws <- epred_mod_success %>% 
  group_by(.draw, familiarity) %>% 
  summarize(mean_epred = mean(.epred),
            .groups = "drop") 
epred_mod_success_byfamiliarity_draws %>%
  group_by(familiarity) %>% 
  summarize(prop_gt = mean(mean_epred > 0.5),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            hdi_lo = hdi(mean_epred)[ncol(hdi(mean_epred)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_epred = mean(mean_epred),
            hdi_hi = hdi(mean_epred)[ncol(hdi(mean_epred))], # rightmost HDI UB to safeguard against multimodality
            .groups = "drop")
epred_mod_success_byfamiliarity_draws_contrast <- epred_mod_success_byfamiliarity_draws %>% 
  compare_levels(mean_epred, "familiarity")
epred_mod_success_byfamiliarity_draws_contrast %>% 
  summarize(prop_gt = mean(mean_epred > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            hdi_lo = hdi(mean_epred)[ncol(hdi(mean_epred)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_epred = mean(mean_epred),
            hdi_hi = hdi(mean_epred)[ncol(hdi(mean_epred))], # rightmost HDI UB to safeguard against multimodality
            .groups = "drop")

# fig (coordination age results)
# data prep
df_plot2 <- epred_mod_success %>% 
  group_by(.draw, group_size, group_mean_age) %>% 
  summarize(mean_epred = mean(.epred)) %>% 
  ungroup() %>% 
  group_by(group_size, group_mean_age) %>% 
  summarize(prop_gt = mean(mean_epred > 0),
            ci_lo = quantile(mean_epred, .025)[[1]],
            mean_mean_epred = mean(mean_epred),
            ci_hi = quantile(mean_epred, .975)[[1]],
            .groups = "drop")

# fig2 (continuous age)
ggplot(df_plot2,
       aes(x = group_mean_age,
           y = mean_mean_epred,
           fill = group_size,
           color = group_size)) +
  geom_ribbon(aes(ymin = ci_lo,
                  ymax = ci_hi),
              alpha = 0.4, color = NA) +
  geom_line(linewidth = 1.5) +
  theme_classic(base_size = 17,
                base_family = "Times New Roman") +
  labs(x = "Group Age",
       y = "Predicted Success Rate",
       color = "Group Size",
       fill = "Group Size") +
  scale_color_manual(values = c("#97af68", "#CBA1B8"),
                     labels = c("Dyad", "Triad")) +
  scale_fill_manual(values = c("#97af68", "#CBA1B8"),
                    labels = c("Dyad", "Triad")) +
  annotate(
    "text",
    x = 2.46, y = c(.74, .3),
    label = c("Dyad", "Triad"),
    hjust = 1.1,
    angle = c(35, 43),
    family = "Times New Roman",
    fontface = "bold",
    size = 5,
    color = c("#667A42", "#927288")
  ) +
  annotate(
    "text",
    x = age_zero + .05, y = .25,
    label = "Dyad = Triad",
    angle = 90,
    family = "Times New Roman",
    fontface = "bold",
    size = 3.5
  ) +
  geom_vline(xintercept = age_zero, linetype = 2, linewidth = .8, alpha = 1) +
  geom_hline(yintercept = .5, linetype = 2, linewidth = .5, alpha = .5, color = "grey40") +
  scale_y_continuous(labels = function(x) sub("^0+", "", format(x, trim = TRUE)),  # remove leading zeros
                     breaks = pretty_breaks(3)) +
  scale_x_continuous(breaks = pretty_breaks(3)) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5),
        axis.text = element_text(size = 15),
        legend.position = "none")
# ggsave("figs/fig2.png", height = 4, width = 5)

# fig coordination categorical age
fig_coord_cat_age <- ggplot(epred_mod_success_bygroup_draws,
                  aes(x = fct_rev(group_size), y = mean_epred)) +
  stat_halfeye(aes(fill = after_stat(y < 0.5)), .width = 0.95, slab_alpha = 0.6, slab_linewidth = 0.5, slab_color = "black") +
  scale_fill_manual(values = c("TRUE" = "grey80", "FALSE" = "grey30"), guide = "none") +
  geom_text(data = summary_epred_mod_success_bygroup_draws,
            aes(x = group_size, y = hdi_hi + .005, label = prop_gt_char),
            nudge_x = .5,
            size = 4.5,
            vjust = -.6,
            family = "Times New Roman",
            fontface = "bold",
            color = "grey30") +
  geom_hline(yintercept = .5, linetype = 2) +
  facet_grid( ~ age_factor) +
  labs(x = "Group Size",
       y = "Predicted Success Rate") +
  scale_y_continuous(
    labels = function(x) sub("^0+", "", format(x, trim = TRUE)),
    breaks = pretty_breaks(2),
    limits = c(NA, 1.03)
  ) +
  theme_classic(base_size = 17, base_family = "Times New Roman") +
  theme(axis.text = element_text(size = 15))
# ggsave("figs/fig_coord_cat_age.png", height = 5, width = 8)

# contrasts
# across trial type
epred_mod_success_bygroup_draws_contrasts <- epred_mod_success_bygroup_draws %>% 
  mutate(group = factor(case_when(age_factor == "2-Year-Olds" & group_size == "Dyad" ~ "2-yo Dyad",
                                  age_factor == "3-Year-Olds" & group_size == "Dyad" ~ "3-yo Dyad",
                                  age_factor == "2-Year-Olds" & group_size == "Triad" ~ "2-yo Triad",
                                  age_factor == "3-Year-Olds" & group_size == "Triad" ~ "3-yo Triad"))) %>%
  compare_levels(mean_epred, by = "group") %>%
  ungroup() %>% 
  rename(diff_mean_epred = mean_epred)
epred_mod_success_bygroup_draws_contrasts_table <- epred_mod_success_bygroup_draws_contrasts %>%
  group_by(group) %>% 
  summarize(prop_gt = mean(diff_mean_epred > 0),
            hdi_lo = hdi(diff_mean_epred)[ncol(hdi(diff_mean_epred)) - 1],
            mean_diff_mean_epred = mean(diff_mean_epred),
            hdi_hi = hdi(diff_mean_epred)[ncol(hdi(diff_mean_epred))],
            .groups = "drop")
```

## Communication
### Predicting Coordination
```{r coordination communication} 
# draws for coordination communication analysis
epred_mod_success_comm_draws <- epred_mod_success_comm %>%
  group_by(.draw, group_size, n_inits_perprompt) %>% 
  summarize(comm_slope = mean(.epred),
            .groups = "drop")

epred_mod_success_comm_draws_summary <- epred_mod_success_comm_draws %>% 
  group_by(group_size, n_inits_perprompt) %>% 
  summarize(prop_gt = mean(comm_slope > .5),
            ci_lo = quantile(comm_slope, .025),
            hdi_lo = hdi(comm_slope)[1], # rightmost HDI LB to safeguard against multimodality
            mean_age_slope = mean(comm_slope),
            ci_hi = quantile(comm_slope, .975),
            hdi_hi = hdi(comm_slope)[2], # rightmost HDI LB to safeguard against multimodality
            .groups = "drop")

# fig3 (success predicted by communication)
ggplot(epred_mod_success_comm_draws_summary,
       aes(x = n_inits_perprompt,
           y = mean_age_slope,
           fill = group_size,
           color = group_size)) +
  geom_ribbon(aes(ymin = ci_lo,
                  ymax = ci_hi),
              alpha = 0.4, color = NA) +
  geom_line(linewidth = 1.5) +
  theme_classic(base_size = 17,
                base_family = "Times New Roman") +
  labs(x = "References to Keys",
       y = "Predicted Success Rate",
       color = "Group Size",
       fill = "Group Size") +
  scale_color_manual(values = c("#97af68", "#CBA1B8"),
                     labels = c("Dyad", "Triad")) +
  scale_fill_manual(values = c("#97af68", "#CBA1B8"),
                    labels = c("Dyad", "Triad")) +
  annotate(
    "text",
    x = c(.41, .32) , y = c(.93, .77),
    label = c("Dyad", "Triad"),
    hjust = 1.1,
    angle = c(12, 50),
    family = "Times New Roman",
    fontface = "bold",
    size = 5,
    color = c("#667A42", "#927288")
  ) +
  # geom_hline(yintercept = .5, linetype = 2) +
  geom_hline(yintercept = .5, linetype = 2, linewidth = .5, alpha = .5, color = "grey40") +
  scale_x_continuous(breaks = pretty_breaks(2)) +
  scale_y_continuous(labels = function(x) sub("^(-?)0\\.", "\\1.", sprintf("%.1f", x)),
                     breaks = pretty_breaks(2)) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5),
        axis.text = element_text(size = 15),
        legend.position = "none")
# ggsave("figs/fig3.png", height = 4, width = 5)
```

```{r coordination communication-group size}
epred_mod_success_comm1 <- epred_mod_success_comm %>% 
  group_by(.draw, group_size) %>% 
  summarize(age_slope = cov(n_inits_perprompt, .epred) / var(n_inits_perprompt),
            .groups = "drop") 

epred_mod_success_comm1 %>% 
  group_by(group_size) %>% 
    summarize(prop_gt = mean(age_slope > 0),
            hdi_lo = hdi(age_slope)[1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_epred = mean(age_slope),
            hdi_hi = hdi(age_slope)[2], # rightmost HDI LB to safeguard against multimodality
            .groups = "drop")

# dyads' vs. triads' age slopes (triads > dyads)
epred_mod_success_comm1 %>% 
  compare_levels(age_slope, by = "group_size") %>% 
  rename(diff_age_slope = age_slope) %>% 
  group_by(group_size) %>% 
  summarize(prop_gt = mean(diff_age_slope > 0),
            hdi_lo = hdi(diff_age_slope)[1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_epred = mean(diff_age_slope),
            hdi_hi = hdi(diff_age_slope)[2], # rightmost HDI LB to safeguard against multimodality
            .groups = "drop")
```

### Predicting Communication
#### Data Preparation
```{r communication data preparation}
df_comm <- tsa_data %>% 
  group_by(group_id, age_factor, outcome) %>% 
  summarize(mean = mean(n_inits_perprompt)) %>% 
  mutate(outcome = str_to_title(outcome),
         age_factor = paste0(age_factor, "-Year-Olds"))

fig_comm <- df_comm %>% 
  ggplot(aes(y = fct_rev(outcome), x = mean)) + 
  facet_grid(age_factor~ .) +
  geom_jitter(width = .2, 
              height = 0.2, 
              alpha = 0.6, 
              size = 3, 
              color = "#97af68") +
  theme_classic(base_family = "Times New Roman", 
                base_size = 17) +
  labs(y = NULL, 
       x = "Average Reference Rate") +
  stat_summary(fun = mean,
               geom = "crossbar",
               color = "black",
               linewidth = 0.5,
               width = .75) 

tsa_data %>% group_by(outcome, age_factor) %>% # check
  summarize(n = n(),
            mean = mean(communication),
            sd = sd(communication),
            .groups = "drop")

tsa_data %>% # lots of low values in outcome == successful
  ggplot(aes(x = communication)) +
  geom_histogram() +
  facet_grid(. ~ outcome)

tsa_data %>% # mean ~= variance
  summarize(mean = mean(communication),
            variance = var(communication)) %>% 
  mutate(ratio = variance / mean) # ideally, equals 1 -- values greater than 1 signals overdispersion

# communication by location
tsa_data %>% 
  group_by(location) %>% 
  summarize(mean = mean(communication),
            sd = sd(communication))

# communication by familiarity
tsa_data %>% 
  group_by(familiarity) %>% 
  summarize(mean = mean(communication),
            sd = sd(communication))
```

#### Model
```{r communication model}
# we use poisson because zero-inflated negative binomial model (brms "zero_inflated_negbinomial()") indicated neither zero inflation nor overdispersion

mod_comm <- func_brm(formula = communication ~ (group_mean_age_standardized + outcome + group_size)^2 + familiarity + location + offset(log(prompt)) + (outcome | group_id) + (1 | trial),
                     data = tsa_data,
                     family = poisson(),
                     prior = c(prior(normal(log(.5), 2), class = Intercept),
                               prior(normal(0, 0.25), class = b),            
                               prior(normal(0, .15), class = sd),         
                               prior(lkj(2), class = cor)))
```

#### Posterior Checks
```{r communication posterior checks}
# plot(mod_comm)
# pp_check(mod_comm, ndraws = 100)
# pp_check(mod_comm, "ecdf_overlay", ndraws = 1000)
# conditional_effects(mod_comm, effects = "age_factor:outcome")

func_bayesian_p_val(mod = mod_comm, responsevar = "communication") # poisson p val checks out
```

#### Results
##### Posterior Draws
```{r communication posterior draws}
newdata_mod_comm <- crossing(group_size = (levels(mod_comm$data$group_size)),
                             location = levels(mod_comm$data$location),
                             familiarity = levels(mod_comm$data$familiarity),
                             group_mean_age_standardized = seq(from = min(mod_comm$data$group_mean_age_standardized), 
                                                               to = max(mod_comm$data$group_mean_age_standardized), 
                                                               length.out = n_length),  
                             outcome = levels(mod_comm$data$outcome),
                             prompt = seq(from = min(mod_comm$data$prompt), 
                                          to = max(mod_comm$data$prompt))) %>% 
  mutate(across(c(group_size, location), ~as.factor(.)))

# draw posterior samples
epred_mod_comm <- local({
  set.seed(27707) # reproducible subsampling of posterior draws
  epred_draws(mod_comm, # draws of posterior model-predicted success rate
              newdata_mod_comm,
              re_formula = NA, # generate predictions per trial level, marginalized across what we've learned about group-level variance (i.e., the other random intercept)
              ndraws = n_epred_draws)
}) %>%
  ungroup() %>%
  mutate(across(c(group_size, outcome, location), ~str_to_title(.)),
         group_mean_age = group_mean_age_standardized * sd(tsa_data$group_mean_age) + mean(tsa_data$group_mean_age),
         age_factor = factor(ifelse(group_mean_age >= 3, "3-Year-Olds", "2-Year-Olds")),
         rate = .epred / prompt) # get poisson rate
```

##### Categorical Age
```{r communication categorical age}
epred_mod_comm_age_draws <- epred_mod_comm %>% 
  group_by(.draw, age_factor) %>% 
  summarize(mean_rate = mean(rate),
            .groups = "drop")

epred_mod_comm_age_draws %>% 
  group_by(age_factor) %>% 
  summarize(hdi_lo = hdi(mean_rate)[ncol(hdi(mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_rate = mean(mean_rate),
            hdi_hi = hdi(mean_rate)[ncol(hdi(mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")

epred_mod_comm_age_draws_constrasts <- epred_mod_comm_age_draws %>% 
  group_by(age_factor) %>% 
  compare_levels(mean_rate, by = "age_factor") %>% 
  ungroup() %>% 
  rename(diff_mean_rate = mean_rate)

# 3-year-olds talk more than 2-year-olds
epred_mod_comm_age_draws_constrasts %>% 
  group_by(age_factor) %>% 
  summarize(hdi_lo = hdi(diff_mean_rate)[ncol(hdi(diff_mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_diff_mean_rate = mean(diff_mean_rate),
            hdi_hi = hdi(diff_mean_rate)[ncol(hdi(diff_mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(diff_mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")
```

##### Location
```{r communication location}
epred_mod_comm_loc_draws <- epred_mod_comm %>% 
  group_by(.draw, location) %>% 
  summarize(mean_rate = mean(rate),
            .groups = "drop")

epred_mod_comm_loc_draws %>% 
  group_by(location) %>% 
  summarize(hdi_lo = hdi(mean_rate)[ncol(hdi(mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_rate = mean(mean_rate),
            hdi_hi = hdi(mean_rate)[ncol(hdi(mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")

epred_mod_comm_loc_draws_contrasts <- epred_mod_comm_loc_draws %>% 
  group_by(location) %>% 
  compare_levels(mean_rate, by = "location") %>% 
  ungroup() %>% 
  rename(diff_mean_rate = mean_rate)

epred_mod_comm_loc_draws_contrasts %>% 
  group_by(location) %>% 
  summarize(hdi_lo = hdi(diff_mean_rate)[ncol(hdi(diff_mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_diff_mean_rate = mean(diff_mean_rate),
            hdi_hi = hdi(diff_mean_rate)[ncol(hdi(diff_mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(diff_mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")
```

##### Familiarity
```{r communication location}
epred_mod_comm_fam_draws <- epred_mod_comm %>% 
  group_by(.draw, familiarity) %>% 
  summarize(mean_rate = mean(rate),
            .groups = "drop")

epred_mod_comm_fam_draws %>% 
  group_by(familiarity) %>% 
  summarize(hdi_lo = hdi(mean_rate)[ncol(hdi(mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_rate = mean(mean_rate),
            hdi_hi = hdi(mean_rate)[ncol(hdi(mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")

epred_mod_comm_fam_draws_contrasts <- epred_mod_comm_fam_draws %>% 
  mutate(familiarity = fct_relevel(familiarity, "unfamiliar", "familiar")) %>% 
  group_by(familiarity) %>% 
  compare_levels(mean_rate, by = "familiarity") %>% 
  ungroup() %>% 
  rename(diff_mean_rate = mean_rate)

epred_mod_comm_fam_draws_contrasts %>% 
  group_by(familiarity) %>% 
  summarize(hdi_lo = hdi(diff_mean_rate)[ncol(hdi(diff_mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_diff_mean_rate = mean(diff_mean_rate),
            hdi_hi = hdi(diff_mean_rate)[ncol(hdi(diff_mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(diff_mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")
```

##### Outcome
```{r communication outcome}
# organize draws
epred_mod_comm_draws_conditional <- epred_mod_comm %>% # posterior rate of key references per prompt
  group_by(.draw, outcome, age_factor) %>% 
  summarize(mean_rate = mean(rate), .groups = "drop")

epred_mod_comm_draws_overall <- epred_mod_comm %>% # posterior rate of key references per prompt
  group_by(.draw, outcome) %>% 
  summarize(mean_rate = mean(rate), .groups = "drop")

epred_mod_comm_draws <- rbind(epred_mod_comm_draws_conditional,
                              epred_mod_comm_draws_overall %>% mutate(age_factor = "Overall"))

# summaries
epred_mod_comm_draws_conditional_summary <- epred_mod_comm_draws_conditional %>% # conditional on age
  group_by(outcome, age_factor) %>%
  summarize(hdi_lo = hdi(mean_rate)[ncol(hdi(mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_rate = mean(mean_rate),
            hdi_hi = hdi(mean_rate)[ncol(hdi(mean_rate))], # rightmost HDI UB to safeguard against multimodality
            .groups = "drop")
epred_mod_comm_draws_overall_summary <- epred_mod_comm_draws_overall %>% # marginal across age
  group_by(outcome) %>%
  summarize(hdi_lo = hdi(mean_rate)[ncol(hdi(mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_rate = mean(mean_rate),
            hdi_hi = hdi(mean_rate)[ncol(hdi(mean_rate))], # rightmost HDI UB to safeguard against multimodality
            .groups = "drop")
epred_mod_comm_draws_summary <- rbind(epred_mod_comm_draws_conditional_summary,
                                      epred_mod_comm_draws_overall_summary %>% mutate(age_factor = "Overall"))

# contrasts
epred_mod_comm_draws_conditional_contrasts <- epred_mod_comm_draws_conditional %>% # successful 2-year-old groups referred to the keys more often than unsuccessful groups; 3-yo groups showed no association
  group_by(age_factor) %>% 
  compare_levels(mean_rate, by = "outcome") %>% 
  ungroup() 
epred_mod_comm_draws_conditional_contrasts_summary <- epred_mod_comm_draws_conditional_contrasts %>% 
  group_by(age_factor) %>% 
  summarize(hdi_lo = hdi(mean_rate)[ncol(hdi(mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_rate = mean(mean_rate),
            hdi_hi = hdi(mean_rate)[ncol(hdi(mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")

epred_mod_comm_draws_overall_contrasts <- epred_mod_comm_draws_overall %>% 
  mutate(outcome = fct_relevel(outcome, "Unsuccessful", "Successful")) %>% 
  compare_levels(mean_rate, by = "outcome") %>% 
  ungroup()
epred_mod_comm_draws_overall_contrasts_summary <- epred_mod_comm_draws_overall_contrasts %>% 
  group_by(outcome) %>% 
  summarize(hdi_lo = hdi(mean_rate)[ncol(hdi(mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
          mean_mean_rate = mean(mean_rate),
          hdi_hi = hdi(mean_rate)[ncol(hdi(mean_rate))], # rightmost HDI UB to safeguard against multimodality
          prop_gt = mean(mean_rate > 0),
          prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
          .groups = "drop")

epred_mod_comm_draws_contrasts <- rbind(epred_mod_comm_draws_conditional_contrasts,
                                        epred_mod_comm_draws_overall_contrasts %>% mutate(age_factor = "Overall"))
epred_mod_comm_draws_contrasts_summary <- rbind(epred_mod_comm_draws_conditional_contrasts_summary,
                                                epred_mod_comm_draws_overall_contrasts_summary %>% 
                                                  select(-outcome) %>% 
                                                  mutate(age_factor = "Overall"))

# fig_mod_comm (communication model results)
fig_mod_comm <- ggplot(epred_mod_comm_draws_conditional_contrasts,
                aes(y = age_factor, x = mean_rate)) +
  stat_halfeye(aes(fill = after_stat(x < 0)),
               .width = 0.95, slab_alpha = 0.6, slab_linewidth = 0.5, slab_color = "black") +
  scale_fill_manual(values = c("TRUE" = "grey80", "FALSE" = "grey30"), guide = "none") +
  geom_text(data = epred_mod_comm_draws_conditional_contrasts_summary,
            aes(y = age_factor, x = .15, label = prop_gt_char),
            nudge_y = 0.3,
            size  = 4.75,
            family = "Times New Roman",
            fontface = "bold",
            color = "grey30") +
  geom_text(data = data.frame(
    age_factor = "2-Year-Olds",
    x = -.23,
    y = 2.05,
    label = "Successful"),
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE,
    size = 4.75,
    fontface = "bold",
    family = "Times New Roman",
    color = "grey80")+
  geom_text(data = data.frame(
    age_factor = "2-Year-Olds",
    x = 0.28,
    y = 2.05,
    label = "Unsuccessful"),
    aes(x = x, y = y, label = label),
    inherit.aes = FALSE,
    size = 4.75,
    fontface = "bold",
    family = "Times New Roman",
    color = "grey30") +
  facet_grid(age_factor ~ ., scales = "free") +
  labs(x = "Difference in Predicted\nReference Rates",
       y = NULL) +
  geom_vline(xintercept = 0, linetype = 2) +
  scale_x_continuous(breaks = pretty_breaks(3),
                     labels = function(x) round(abs(x), 2),
                     expand = expansion(mult = c(0.1, .25))) +
  scale_y_discrete(expand = expansion(mult = c(0.1, 1.15))) +
  theme_classic(base_size = 17, base_family = "Times New Roman") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

# ggsave("figs/fig_mod_comm.png", height = 4, width = 8)
```

```{r communication condition}
epred_mod_comm_size_draws <- epred_mod_comm %>% 
  group_by(.draw, group_size) %>% 
  summarize(mean_rate = mean(rate),
            .groups = "drop")

epred_mod_comm_size_draws %>% 
  group_by(group_size) %>% 
  summarize(hdi_lo = hdi(mean_rate)[ncol(hdi(mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_mean_rate = mean(mean_rate),
            hdi_hi = hdi(mean_rate)[ncol(hdi(mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")

epred_mod_comm_size_draws_contrasts <- epred_mod_comm_size_draws %>% 
  group_by(group_size) %>% 
  compare_levels(mean_rate, by = "group_size") %>% 
  ungroup() %>% 
  rename(diff_mean_rate = mean_rate)

epred_mod_comm_size_draws_contrasts %>% 
  group_by(group_size) %>% 
  summarize(hdi_lo = hdi(diff_mean_rate)[ncol(hdi(diff_mean_rate)) - 1], # rightmost HDI LB to safeguard against multimodality
            mean_diff_mean_rate = mean(diff_mean_rate),
            hdi_hi = hdi(diff_mean_rate)[ncol(hdi(diff_mean_rate))], # rightmost HDI UB to safeguard against multimodality
            prop_gt = mean(diff_mean_rate > 0),
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
            .groups = "drop")
```

## Strategies
### Data Preparation
```{r strategies data preparation}
# coordination strategies among successful groups
# probability of information as the means to success among successful groups
tsa_data$collab_yesno <- relevel(tsa_data$collab_yesno, ref = "individualistic")
contrasts(tsa_data$collab_yesno) # model the probability of collaboration instead of individualistic as the means of coordination among successful groups

tsa_data_model5a <- tsa_data %>% # exclude unsuccessful outcomes
  filter(outcome == "successful")

tsa_data_model5 <- tsa_data_model5a %>% 
  select(-group_mean_age_standardized) %>% 
  left_join(tsa_data_model5a %>% 
              distinct(group_id, group_mean_age) %>% 
              mutate(group_mean_age_standardized = as.numeric(scale(group_mean_age))))

tsa_data_model5 %>% # strategy proportions among successful groups
  drop_na(strategy) %>% 
  count(strategy) %>% 
  # group_by(age_factor, group_size) %>% 
  mutate(ratio = n / sum(n))

tsa_data_model5 %>% # count of groups who succeeded at least once
  distinct(group_id) %>% 
  count

# fig_strategies data
fig_strat_dat <- tsa_data_model5 %>% 
  filter(collab_yesno == "collaborative") %>% # only display collaboration data, because this is a yes-no mutually exclusive variable
  group_by(collab_yesno, strategy, group_size, age_factor, group_id) %>%
  count %>% 
  ungroup() %>% # don't need to do any recoding here because no groups used a non-informative strategy on all four trials
  mutate(across(c(collab_yesno, group_size), ~str_to_title(.)),
         age_factor_recoded = case_when(age_factor == "2" ~ "2-Year-Olds", 
                                                   age_factor == "3" ~ "3-Year-Olds")) %>% 
  ggplot(aes(x = fct_rev(group_size), y = n)) +
  geom_jitter(width = 0.25, height = 0.1, size = 3, alpha = 0.6, color = "forestgreen") +
  stat_summary(fun = mean, 
               geom = "crossbar", 
               color = "black", 
               alpha = 0.6) +
  facet_grid( ~ age_factor_recoded) + 
  theme_classic(base_size = 17, base_family = "Times New Roman") +
  scale_y_continuous(breaks = 1:4, limits = c(0.75, 4.2)) +
  labs(x = "Group Size",
       y = "Collaboration Count") +
  theme(axis.text = element_text(size = 15))
```

### Model
```{r strategies model}
mod_strategy <- func_brm(formula =  collab_yesno ~ group_size * group_mean_age_standardized + location + (1 | group_id) + (1 | trial),
                         data = tsa_data_model5,
                         priors = model_priors[-4,],
                         family = "bernoulli")
```

### Posterior Checks
```{r strategies posterior checks}
# conditional_effects(mod_strategy, effects = "group_mean_age_standardized:group_size")
# plot(mod_strategy) # trace plots
# pp_check(mod_strategy, type = "bars_grouped", group = "group_size", ndraws = 100)
func_bayesian_p_val(mod = mod_strategy, responsevar = "collab_yesno")
```

### Results
#### Posterior Draws
```{r strategies posterior draws}
newdata_mod_strategy <- crossing(group_size = levels(mod_strategy$data$group_size) %>% fct_unique() %>% fct_drop(),
                               location     = levels(mod_strategy$data$location) %>% fct_unique() %>% fct_drop(),
                               group_mean_age_standardized  = seq(from = min(mod_strategy$data$group_mean_age_standardized),
                                                                  to = max(mod_strategy$data$group_mean_age_standardized),
                                                                  length.out = n_length))

epred_mod_strategy <- local({
  set.seed(27707) # reproducible subsampling of posterior draws
  epred_draws(mod_strategy, # draws of posterior model-predicted success rate
                                newdata_mod_strategy,
                                re_formula = NA, 
                                ndraws = n_epred_draws)
  }) %>% 
  ungroup %>% 
  mutate(group_mean_age = group_mean_age_standardized * sd(tsa_data_model5$group_mean_age) + mean(tsa_data_model5$group_mean_age),
         age_factor = factor(ifelse(group_mean_age >= 3, "3-Year-Olds", "2-Year-Olds")), # make categorical age var
         group_size = factor(str_to_title(as.character(group_size))),
         group = factor(case_when(age_factor == "2-Year-Olds" & group_size == "Dyad" ~ "2-yo Dyad",
                                  age_factor == "3-Year-Olds" & group_size == "Dyad" ~ "3-yo Dyad",
                                  age_factor == "2-Year-Olds" & group_size == "Triad" ~ "2-yo Triad",
                                  age_factor == "3-Year-Olds" & group_size == "Triad" ~ "3-yo Triad"),
                        levels = c("3-yo Dyad", "3-yo Triad", "2-yo Dyad", "2-yo Triad")))
```

#### Categorical Age
```{r strategies categorical age}
# Custom analytical function
func_epred_processing <- function(df, var1, var2 = NULL){ 
  
  var1 <- rlang::enquo(var1)
  var2 <- rlang::enquo(var2)
  
  draws <- df %>% 
    group_by(.draw, {{var1}}, {{var2}}) %>% 
    summarize(mean_epred = mean(.epred), .groups = "drop")
  
  draws_summary <- draws %>% 
    group_by({{var1}}, {{var2}}) %>% 
    summarize(hdi_lo = hdi(mean_epred)[ncol(hdi(mean_epred)) - 1], # rightmost HDI LB to safeguard against multimodality
              mean_mean_epred = mean(mean_epred),
              hdi_hi = hdi(mean_epred)[ncol(hdi(mean_epred))], # rightmost HDI UB to safeguard against multimodality
              prop_gt = mean(mean_epred > 0.5),
              prop_gt_char = sprintf("%.0f%%", 100 * prop_gt),
              .groups = "drop")
  
  contrasts_draws <- draws %>%
    group_by({{var2}}) %>%
    compare_levels(mean_epred, by = {{var1}}) %>%
    ungroup() %>%
    rename(diff_mean_epred = mean_epred)
  
  contrasts_draws_summary <- contrasts_draws %>%
    group_by({{var1}}, {{var2}}) %>%
    summarize(hdi_lo = hdi(diff_mean_epred)[ncol(hdi(diff_mean_epred)) - 1], # rightmost HDI LB to safeguard against multimodality
              mean_diff_mean_epred = mean(diff_mean_epred),
              hdi_hi = hdi(diff_mean_epred)[ncol(hdi(diff_mean_epred))], # rightmost HDI UB to safeguard against multimodality
              prop_gt = mean(diff_mean_epred > 0),
              .groups = "drop")
  
  if (!rlang::quo_is_null(var2)) { 
    contrasts_draws_intxn <- contrasts_draws %>%
      compare_levels(diff_mean_epred, by = {{var2}}) %>%
      ungroup() %>%
      rename(diff_diff_mean_epred = diff_mean_epred)
    
    contrasts_draws_intxn_summary <- contrasts_draws_intxn %>%
      summarize(hdi_lo = hdi(diff_diff_mean_epred)[ncol(hdi(diff_diff_mean_epred)) - 1],
                mean_diff_diff_mean_epred = mean(diff_diff_mean_epred),
                hdi_hi = hdi(diff_diff_mean_epred)[ncol(hdi(diff_diff_mean_epred))],
                prop_gt = mean(diff_diff_mean_epred > 0),
                .groups = "drop")
    
    return(list(draws = draws, draws_summary = draws_summary, contrasts_draws = contrasts_draws, contrasts_draws_summary = contrasts_draws_summary, contrasts_draws_intxn = contrasts_draws_intxn, contrasts_draws_intxn_summary = contrasts_draws_intxn_summary))
  } 
  else {return(list(draws = draws, draws_summary = draws_summary, contrasts_draws = contrasts_draws, contrasts_draws_summary = contrasts_draws_summary))
  }
}

# Results
epred_processing_group_mod_strategy <- func_epred_processing(epred_mod_strategy, group) # means and contrasts for all cells
epred_processing_group_size_mod_strategy <- func_epred_processing(epred_mod_strategy, group_size) # means and contrasts for group size
epred_processing_age_factor_mod_strategy <- func_epred_processing(epred_mod_strategy, age_factor) # means and contrasts for age
epred_processing_interaction1_mod_strategy <- func_epred_processing(epred_mod_strategy, group_size, age_factor) # means and contrasts for group size:age (interaction estimate is equivalent for interaction1 and interaction2 -- think, equality of mixed partials!)
epred_processing_interaction2_mod_strategy <- func_epred_processing(epred_mod_strategy, age_factor, group_size) # means and contrasts for age:group size (interaction estimate is equivalent for interaction1 and interaction2 -- think, equality of mixed partials!)

# fig4 (strategies results)
df_fig4 <- list(draws = epred_processing_group_mod_strategy$draws, # data preparation
                 draws_summary = epred_processing_group_mod_strategy$draws_summary) %>% 
  map(~ .x %>% 
        separate(group, into = c("age_factor", "group_size"), sep = " ") %>% 
        mutate(age_factor = case_when(age_factor == "2-yo" ~ "2-Year-Olds",
                                                 age_factor == "3-yo" ~ "3-Year-Olds",
                                                 TRUE ~ NA_character_)))
        
ggplot(df_fig4$draws,
                  aes(x = fct_rev(group_size), y = mean_epred)) +
  stat_halfeye(aes(fill = after_stat(y < 0.5)), .width = 0.95, slab_alpha = 0.6, slab_linewidth = 0.5, slab_color = "black") +
  scale_fill_manual(values = c("TRUE" = "grey80", "FALSE" = "grey30"), guide = "none") +
  geom_text(data = df_fig4$draws_summary,
            aes(x = group_size, y = hdi_hi + .005, label = prop_gt_char),
            nudge_x = .5,
            size = 4.5,
            vjust = -.6,
            family = "Times New Roman",
            fontface = "bold",
            color = "grey30") +
  geom_hline(yintercept = .5, linetype = 2) +
  facet_grid( ~ age_factor) +
  labs(x = "Group Size",
       y = "Predicted Collaboration Rate") +
  scale_y_continuous(
    labels = function(x) sub("^0+", "", format(x, trim = TRUE)),
    breaks = pretty_breaks(2),
    limits = c(NA, 1.03)
  ) +
  theme_classic(base_size = 17, base_family = "Times New Roman") +
  theme(axis.text = element_text(size = 15))
# ggsave("figs/fig4.png", height = 3, width = 5)
```

## Color
### Data Preparation
```{r color data preparation}
tsa_data_color <- tsa_data %>% drop_na(color_pattern)
tsa_data_color %>% 
  count(age_factor, group_size, color_pattern)
```

### Model
```{r color model}
mod_color <- func_brm(formula = color_pattern ~ group_size * group_mean_age_standardized + location,
                      data = tsa_data_color,
                      family = "categorical"(refcat = "no_pattern"),
                      priors = c(set_prior("normal(0, 1.00)", class = "Intercept", dpar = "mualternate"),
                                 set_prior("normal(0, 1.00)", class = "Intercept", dpar = "mufirstsuccessful"),
                                 set_prior("normal(0, .70)", class = "b", dpar = "mualternate"),
                                 set_prior("normal(0, .70)", class = "b", dpar = "mufirstsuccessful")))
```

### Posterior Checks
```{r color posterior checks}
# pp_check(mod_color, type = "bars_grouped", group = "group_size", ndraws = 100)
# plot(mod_color)

# p values
yrep <- posterior_predict(mod_color)
yrep_props <- apply(yrep, # matrix to vectorize function over
                    1, # rowwise vectorization
                    function(x) as.data.frame(prop.table(table(factor(x)))) %>% 
                      mutate(Var1 = case_when(Var1 == 1 ~ attr(yrep, "levels")[1], # get the internal level assigned to 1
                                              Var1 == 2 ~ attr(yrep, "levels")[2], # same for 2
                                              Var1 == 3 ~ attr(yrep, "levels")[3], # same for 3
                                              T ~ NA))) 

yrep_props_tibble0 <- bind_rows(yrep_props, .id = "draw") %>% # convert list to tibble
  as_tibble() %>% 
  rename(response = Var1, # rename vars
         predicted_proportion = Freq)

yrep_props_tibble0 %>% # sometimes, posterior_predict will generate zero counts for a category within a simulated dataset. this quantifies the number of times that that happened.
  count(response) %>% 
  mutate(zero_predicted = dim(yrep)[1] - n) # number of simulated datasets without that category represented

yrep_props_tibble <- yrep_props_tibble0 %>% # account for the zeros, above
  complete(draw, response, fill = list(predicted_proportion = 0)) %>% 
  left_join(
    tibble(response = mod_color$data[["color_pattern"]]) %>% # get observed data
      count(response, name = "observed_n") %>% # count up the observed responses by category
      mutate(observed_proportion = observed_n / sum(observed_n))) %>% # compute observed proportion
  mutate(prediction_exceeds_observation = ifelse(predicted_proportion > observed_proportion, 1, 0)) # compute whether predicted exceeds observed

mod_color_p_vals <- yrep_props_tibble %>% group_by(response) %>% summarize(bayes_p_val = mean(prediction_exceeds_observation)) # compute category-wise bayesian p-values
```

### Results
#### Posterior Draws
```{r color posterior draws}
newdata_mod_color <- crossing(group_size = mod_color$data$group_size %>% fct_unique() %>% fct_drop(),
                              location = mod_color$data$location %>% fct_unique() %>% fct_drop(),
                              group_mean_age_standardized = seq(from = min(mod_color$data$group_mean_age_standardized),
                                                                to = max(mod_color$data$group_mean_age_standardized),
                                                                length.out = 20))

tibble(posterior_samples(mod_color) %>% 
  select(contains("Triad") & contains("mufirstsuccessful"))) %>% 
  clean_names() %>% 
  summarize(hdi = hdi(b_mufirstsuccessful_group_sizetriad_group_mean_age_standardized),
            mean = mean(b_mufirstsuccessful_group_sizetriad_group_mean_age_standardized))

epred_mod_color <- local({
  set.seed(27707) # reproducible subsampling of posterior draws
  epred_draws(mod_color, newdata = newdata_mod_color, ndraws = n_epred_draws)
}) %>% 
  ungroup %>% 
  mutate(group_mean_age = group_mean_age_standardized * sd(tsa_data$group_mean_age) + mean(tsa_data$group_mean_age),
         age_factor = factor(ifelse(group_mean_age >= 3, "3-Year-Olds", "2-Year-Olds")), # make categorical age var
         group_size = factor(str_to_title(as.character(group_size))),
         group = factor(case_when(age_factor == "2-Year-Olds" & group_size == "Dyad" ~ "2-yo Dyad",
                                  age_factor == "3-Year-Olds" & group_size == "Dyad" ~ "3-yo Dyad",
                                  age_factor == "2-Year-Olds" & group_size == "Triad" ~ "2-yo Triad",
                                  age_factor == "3-Year-Olds" & group_size == "Triad" ~ "3-yo Triad"),
                        levels = c("3-yo Dyad", "3-yo Triad", "2-yo Dyad", "2-yo Triad")),
         .category = case_when(.category == "alternate" ~ "Alternate",
                               .category == "first_successful" ~ "First Suc.",
                               .category == "no_pattern" ~ "No Pattern",
                               T ~ NA))
```

#### Categorical Age
```{r color categorical age}
epred_mod_color_draws <- epred_mod_color %>% 
  group_by(.draw, group_size, age_factor, .category) %>% 
  summarize(mean_epred = mean(.epred)) %>% 
  ungroup()

epred_mod_color_draws_contrasts <- epred_mod_color_draws %>% 
  group_by(group_size, age_factor) %>% 
  compare_levels(mean_epred, ".category") 

chance_strat <- .2895975 # see supplement for computation of chance

epred_mod_color_draws_summary <- epred_mod_color_draws %>% 
  group_by(age_factor, group_size, .category) %>% 
  summarize(prop_gt = mean(mean_epred > chance_strat), 
            hdi_lo = hdi(mean_epred)[ncol(hdi(mean_epred)) - 1],
            mean_mean_epred = mean(mean_epred),
            hdi_hi = hdi(mean_epred)[ncol(hdi(mean_epred))],
            prop_gt_char = sprintf("%.0f%%", 100 * prop_gt))
            
epred_mod_color_draws_contrasts %>% 
  group_by(age_factor, group_size, .category) %>% 
  summarize(prop_gt = mean(mean_epred > 0),
            hdi_lo = quantile(mean_epred)[ncol(hdi(mean_epred)) - 1],
            mean_mean_epred = mean(mean_epred),
            hdi_hi = hdi(mean_epred)[ncol(hdi(mean_epred))]) %>% 
  ungroup()

# fig5
tsa_data_color %>% 
  mutate(age_factor = paste0(age_factor, "-Year-Olds"),
         group_size = str_to_title(group_size),
         color_pattern = case_when(color_pattern == "alternate" ~ "Alternate",
                                   color_pattern == "first_successful" ~ "First Suc.",
                                   color_pattern == "no_pattern" ~ "No Pattern")) %>% 
  ggplot(aes(y = color_pattern)) +
  geom_bar(fill = "forestgreen") +
  facet_grid(group_size ~ age_factor) +
  theme_classic(base_size = 17, base_family = "Times New Roman") +
  scale_x_continuous(breaks = c(0, 2, 4, 6, 8)) +
  labs(x = "Number of Groups",
       y = "Color Strategy") +
  theme(axis.text = element_text(size = 15))
# ggsave("figs/fig5.png", height = 3, width = 5)

fig_color <- ggplot(epred_mod_color_draws,
                aes(y = .category, x = mean_epred)) +
  stat_halfeye(aes(fill = after_stat(x < chance_strat)), .width = 0.95, slab_alpha = 0.6, slab_linewidth = 0.5, slab_color = "black") +
  scale_fill_manual(values = c("TRUE" = "grey80", "FALSE" = "grey30"), guide = "none") +
  geom_text(data = epred_mod_color_draws_summary,
            aes(y = .category, x = hdi_hi + .03, label = prop_gt_char),
            nudge_x = .1,
            size = 4.5,
            vjust = -.8,
            family = "Times New Roman",
            fontface = "bold",
            color = "grey30") +
  geom_vline(xintercept = chance_strat, linetype = 2, linewidth = .5, alpha = .5, color = "grey40") +
  facet_grid(group_size ~ age_factor, scales = "free") +
  labs(x = "Predicted Rate",
       y = "Color Strategy") +
  scale_x_continuous(
    labels = function(x) sub("^0+", "", format(x, trim = TRUE)),
    breaks = c(0, round(chance_strat, 2), .75),
    limits = c(NA, 1.03)
  ) +
  theme_classic(base_size = 17, base_family = "Times New Roman") +
  theme(axis.text = element_text(size = 14))
# ggsave("figs/sup_fig3.png", height = 5, width = 6)
```

```{r supplementary tables}
# Create custom table functions, model lists
func_sup_tab <- function(df){
  flextable(df) %>% 
    autofit() %>% # shrink to fit content
    font(fontname = "Times New Roman", part = "all") %>% # font
    fontsize(size = 11, part = "all") %>% # font size
    set_table_properties(width = 1, layout = "autofit") %>% # scale to page width
    border_remove() %>% # remove all borders first
    hline(i = 1, border = fp_border_default(), part = "header") %>% # line below header
    align(align = "center", part = "all") # center all cells
}

func_mod_tab <- function(model){
  diag_df <- summarise_draws(model) %>%
    filter(str_starts(variable, "b_")) %>%
    select(parameter = variable, ess_bulk, rhat) %>% 
    mutate(ess_bulk = round(ess_bulk, 0),
           rhat = round(rhat, 2))
  as_draws_df(model) %>%  # model posterior fixed effects
    select(starts_with("b_")) %>% 
    pivot_longer(everything(), names_to = "parameter") %>%
    group_by(parameter) %>% 
    summarize(mean = mean(value),
              sd = sd(value),
              q2.5 = quantile(value, 0.025),
              q97.5 = quantile(value, 0.975),
              .groups = "drop") %>% 
    left_join(diag_df, by = "parameter") %>%
    mutate(across(c(mean, sd, q2.5, q97.5, rhat), ~ formatC(.x, format = "f", digits = 2)),
           parameter = str_to_title(str_replace_all(str_replace_all(str_remove_all(parameter, "b_"), "_", " "), ":", " : ")),
           parameter = str_replace_all(parameter, "Locationschool", "Location (School)"),
           parameter = str_replace_all(parameter, "Mualternate", "(Alternate)"),
           parameter = str_replace_all(parameter, "Mufirstsuccessful", "(First Suc.)"),
           parameter = str_replace_all(parameter, "Sizetriad", "Size (Triad)"),
           parameter = str_replace_all(parameter, "N Inits Perprompt Stand", "Communication"),
           parameter = str_replace_all(parameter, "Familiarityunfamiliar", "Familiar. (Unfam.)"),
           parameter = str_remove_all(parameter, "Standardized"),
           parameter = str_replace_all(parameter, "Age Factor3", "Group Mean Age (3-yo's)"),
           parameter = str_replace_all(parameter, "Prop", "Proportion"),
           parameter = str_replace_all(parameter, "Outcomesuccessful", "Outcome"),
           parameter = str_replace_all(parameter, "Recoded1", "(1)"),
           parameter = str_replace_all(parameter, "Recoded2p", "(2+)")) %>% 
    rename_with(~ stringr::str_replace_all(.x, "_", " "), everything()) %>% 
    rename_with(stringr::str_to_title, everything()) %>% 
    rename(SD = Sd, ESS = "Ess Bulk", "R-Hat" = Rhat)
}

mods_list <- list("Engagement" = mod_engagement, 
                  "Coordination" = mod_success, 
                  "Coordination-Comm." = mod_success_comm, 
                  "Communication" = mod_comm, 
                  "Strategy" = mod_strategy, 
                  "Color" = mod_color)

# sup_tab1 (model formulas)
sup_tab1 <- map_dfr(mods_list,
                    ~ as_tibble(paste(deparse(.x$formula$formula), 
                                      collapse = "") %>% # remove extra line added by deparse()
                                  str_squish()) %>% # remove extra whitespace
                      mutate(Observations = nobs(.x), # record observation count
                             Groups = length(unique(.x$data$group_id))),
                    .id = "Model") %>% 
  rename(Formula = value)
sup_tab1_ft <- func_sup_tab(sup_tab1)
# save_as_docx(sup_tab1_ft, path = "tables/sup_tab1.docx")

# sup_tab2 (priors, distributional families, link functions)
sup_tab2 <- map_dfr(mods_list, # perform the following operation on each list item
                    ~ as_tibble(.x$prior) %>% # priors
                      mutate(as_tibble(.x$family[1]), # distributional family
                             as_tibble(.x$family[2])), # link function
                    .id = "model") %>% 
  filter(source == "user") %>% # include only user-specified priors
  select(model, prior, class, dpar, lb, family, link) %>% 
  relocate(family, .after = model) %>% 
  relocate(link, .after = family) %>% 
  rename_with(.fn = ~str_to_title(.), .cols = everything(.)) %>% 
  mutate(across(c(Family, Link), ~ str_to_title(.)))
sup_tab2_ft <- func_sup_tab(sup_tab2)
# save_as_docx(sup_tab2_ft, path = "tables/sup_tab2.docx")

# sup_tab3 (bayesian p values)
sup_tab3 <- tibble(Model = c("Engagement", "Coordination", "Coordination-Comm.", "Communication", "Strategy", "Color (Alternate)", "Color (First Suc.)", "Color (No Pat.)"),
                   "Bayesian p value" = c(func_bayesian_p_val(mod = mod_engagement, responsevar = "engagement_factor"),
                                          func_bayesian_p_val(mod = mod_success, responsevar = "outcome"),
                                          func_bayesian_p_val(mod = mod_success_comm, responsevar = "outcome"),
                                          func_bayesian_p_val(mod = mod_comm, responsevar = "communication"),
                                          func_bayesian_p_val(mod = mod_strategy, responsevar = "collab_yesno"),
                                          mod_color_p_vals %>% filter(response == "alternate") %>% pull(bayes_p_val),
                                          mod_color_p_vals %>% filter(response == "first_successful") %>% pull(bayes_p_val),
                                          mod_color_p_vals %>% filter(response == "no_pattern") %>% pull(bayes_p_val))) %>% 
  mutate(across(starts_with("Bayesian"), ~round(., 2)),
         across(starts_with("Bayesian"), ~sub("^0", "", .x)))
sup_tab3_ft <- func_sup_tab(sup_tab3)
# save_as_docx(sup_tab3_ft, path = "tables/sup_tab3.docx")

# sup_tab4 (posterior parameters)
sup_tab4 <- map_dfr(mods_list, 
                ~ func_mod_tab(.x),
                .id = "Model")
sup_tab4_ft <- func_sup_tab(sup_tab4)
# save_as_docx(sup_tab4_ft, path = "tables/sup_tab4.docx")
```

# Session Info
```{r supplementary tables}
end <- Sys.time()
end - start # script runtime
sessionInfo()
```

# Supplemental Figures
```{r}

```

